Fail Faster

### 2025-12-02 paper/paper.tex

With a sense of two main inefficiences in generator libraries, we set out in this section to investigate solutions.
We begin with a quick tour through multi-stage programming (Section~\ref{subsection:msp}),
then incrementally build \camlname, layering on features and
functionality  (Sections~\ref{subsection:basic-design} through \ref{subsection:type-derived}).
Last, we present a controlled experiment demonstrating how a
faster \rand{} leads to failing faster  (\ref{subsection:faster-rng}).

@@

This covers most of the major functional and functional-adjacent languages with both PBT libraries and metaprogramming capabilities.

>>>>

With a sense of two main inefficiences in generator libraries, we set out in this section to investigate solutions.
We begin with a quick tour through multi-stage programming (Section~\ref{subsection:msp}),
then incrementally build \camlname, layering on features and
functionality  (Sections~\ref{subsection:basic-design} through \ref{subsection:type-derived}).
We begin with simple staging tricks, then move on to more advanced techniques that
leverage our domain-specific understanding of PBT generators.
Last, we present a controlled experiment demonstrating how a
faster \rand{} leads to failing faster  (\ref{subsection:faster-rng}).

@@

This covers a large swath of functional and functional-adjacent languages with both PBT libraries and metaprogramming capabilities,
suggesting that the Allegro technique is widely applicable.
